Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-02-16 papers/intro_paper/discussion.tex
conclusions

Despite these limitations there has been some recent effort to develop parametrizations that could help mapping measurements of the parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0}))$ onto constraints to specific beyond-GR theories. This includes for example the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently applied to LIGO-Virgo GW events in Ref. ~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters, or the proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where deviations from the GR QNMs are mapped onto generic small modifications of the perturbation equations describing the QNMs. Other examples also include proposals to map deviations from the GR QNMs to coefficients in generic effective field theory actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to directly relate measurements of the QNM complex frequencies to a parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which could be used jointly with measurements coming from the Event Horizon Telescope to obtain stronger constraints on deviations from GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
We should note, however, that all these parametrizations are either limited to non-spinning BHs or make use of a series expansion in the BH spin which might limit their accuracy for highly-spinning BHs.

>>>>

Despite these limitations there has been some recent effort to develop parametrizations that could help mapping measurements of the parameters $(\delta f_{\ell m 0}, \delta \tau_{\ell m0})$ onto constraints to specific beyond-GR theories. This includes for example the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently applied to LIGO-Virgo GW events in Ref. ~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters, or the proposal of Refs.~\cite{Cardoso:2019mqo,McManus:2019ulj} where deviations from the GR QNMs are mapped onto generic small modifications of the perturbation equations describing the QNMs. Other examples also include proposals to map deviations from the GR QNMs to coefficients in generic effective field theory actions~\cite{Cardoso:2018ptl,Franciolini:2018uyq,Cano:2020cao} or to directly relate measurements of the QNM complex frequencies to a parametrized non-GR BH metric~\cite{Glampedakis:2017dvb,Suvorov:2021amy,Volkel:2020daa} which could be then used jointly with measurements coming from the Event Horizon Telescope to obtain stronger constraints on deviations from GR~\cite{Volkel:2020daa,Volkel:2020xlc,Psaltis:2020lvx,Yang:2021zqy}.
We should note, however, that all these parametrizations are either limited to non-spinning BHs or make use of a series expansion in the BH spin which might limit their accuracy for highly-spinning BHs.
